\pageId{commands}

\subsection*{\verb|\newcommand| and friends}

SnuggleTeX allows new commands and environments to be defined using the
familiar LaTeX \verb|\newcommand|, \verb|\renewcommand|, \verb|\newenvironment|
and \verb|\renewenvironment| commands. (Note that it does not support the TeX
\verb|\def| command.) These work pretty much the same way as they do in LaTeX.

SnuggleTeX tries to be helpful when reporting error messages that might arise
once these types of commands or environments have been ``evaluated'' (which
essentially amounts to performing text substitutions and then parsing the
results).

\subsubsection*{Examples}

\begin{verbatim}
\newcommand{\mat}[4]{
  \left( 
    \begin{array}{cc}
      #1 & #2 \\
      #3 & #4
    \end{array} 
  \right)
}
\[ A = \mat{\alpha}{\beta}{\gamma}{\delta}\]
\end{verbatim}

creates a handy command for constructing $2\times 2$ matrices
and then outputs one, giving:

\newcommand{\mat}[4]{
  \left( 
    \begin{array}{cc}
      #1 & #2 \\
      #3 & #4
    \end{array} 
  \right)
}
\[ A = \mat{\alpha}{\beta}{\gamma}{\delta}\]

As an example of error reporting, if you paste the above example into the
\href[Try Out]{../tryout.xml} page and add the following line:

\begin{verbatim}
\[ A = \mat{\mat{\silly}{2}{3}{4}}{2}{3}{4} \]
\end{verbatim}

then you would see the following error message:

\begin{verbatim}
Undefined command \silly
At character 39 after "\mat{\silly}{2}{3}{4..." was substituted with "   \left(      \begi..."
At character 39 after "\mat{\mat{\silly}{2}..." was substituted with "   \left(      \begi..."
At line 10, column 8 of input Form Input
\end{verbatim}

\subsection*{Defining Built-in Commands and Environments}

SnuggleTeX also supports defining new Commands and Environments via its Java API.

To do this, you create a \verb|SnugglePackage|, which has a number of methods for
defining new Commands and Environments, along with custom errors codes of your choosing.
This can then be registered to a \verb|SnuggleEngine| using the
\verb|addPackage()| method, making them available to any \verb|SnuggleSession|s
created by the engine.

The most complicated part of this process is specifying how each Command and
Environment should build its branch in the resulting DOM tree. This is done
by you implementing the \verb|CommandHandler| and \verb|EnvironmentHandler| interfaces
as required and using the \verb|DOMBuilder| Object that gets passed
to you to build XHTML, MathML and other XML structures. There are already a lot
of handler classes in the \verb|snuggletex.dombuilding| package that you can
inspect, copy and build on to help here.
