\pageId{maxima}

\newcommand{\ue}[1]{\upConversionExample{#1}}

SnuggleTeX can also attempt to convert input LaTeX to
\href[Maxima]{http://maxima.sourceforge.net/} input syntax.
This is implemented by first \href[converting to Content MathML]{docs://cmathml}.
However, not all inputs that can be successfully converted to
Content MathML can be further converted into Maxima input form. Additional
restrictions on supported inputs are detailed below.

\subsection*{Supported Pre-defined Functions}

All functions supported by the Content MathML up-conversion are supported
here, with the exception of \verb|\log| as Maxima only supports natural
logarithms.

\subsection*{Supported Operators}

All of the operators supported by the Content MathML process are
supported, with the \textbf{exception} of the following relations:

\begin{itemize}
  \item \verb|\equiv|
  \item \verb|\not\equiv|
  \item \verb|\approx|
  \item \verb|\not\approx|
  \item \verb.|.
  \item \verb.\not|.
  \item \verb|\in|
  \item \verb|\not\in|
\end{itemize}

Maxima does not support ``unapplied'' operators symbols, so a LaTeX input
of the form \verb|+| generates a result of the form \verb|operator("+")|
as a rather ad hoc representation of this idea. Similarly, \verb|\not<| results
in \verb|operator("not<")| for want of anything better.
The name of the resulting ``function'' can be specified with
\verb|\setUpConversionOption{maximaOperatorFunction}{name}|.

\ue{\verb|+|}
\ue{\verb|\not=|}
\ue{\verb|\not<|}
\ue{\verb|\setUpConversionOption{maximaOperatorFunction}{silly} $+$|}

\subsection*{Supported Identifiers}

MathML generally allows arbitrary Unicode characters to be used as identifier
names whereas Maxima only safely supports ASCII characters. In terms of LaTeX
input, this means that identifiers input as ``\verb|\something|'' are only supported
if we have discovered a means to convert these into an appropriate Maxima input form.

The identifiers supported so far are:

\begin{tabular}{|c|c|c|}
\hline
LaTeX input & Maxima form & Live Example \\
\hline
\verb|\alpha| & \verb|%alpha| & \ue{\verb|\alpha|} \\
\verb|\beta| & \verb|%beta| & \ue{\verb|\beta|} \\
\verb|\gamma| & \verb|%gamma| & \ue{\verb|\gamma|} \\
\verb|\delta| & \verb|%delta| & \ue{\verb|\delta|} \\
\verb|\epsilon| & \verb|%epsilon| & \ue{\verb|\epsilon|} \\
\verb|\zeta| & \verb|%zeta| & \ue{\verb|\zeta|} \\
\verb|\eta| & \verb|%eta| & \ue{\verb|\eta|} \\
\verb|\theta| & \verb|%theta| & \ue{\verb|\theta|} \\
\verb|\iota| & \verb|%iota| & \ue{\verb|\iota|} \\
\verb|\kappa| & \verb|%kappa| & \ue{\verb|\kappa|} \\
\verb|\lambda| & \verb|%lambda| & \ue{\verb|\lambda|} \\
\verb|\mu| & \verb|%mu| & \ue{\verb|\mu|} \\
\verb|\nu| & \verb|%nu| & \ue{\verb|\nu|} \\
\verb|\xi| & \verb|%xi| & \ue{\verb|\xi|} \\
\verb|\pi| & \verb|%pi| & \ue{\verb|\pi|} \\
\verb|\rho| & \verb|%rho| & \ue{\verb|\rho|} \\
\verb|\sigma| & \verb|%sigma| & \ue{\verb|\sigma|} \\
\verb|\tau| & \verb|%tau| & \ue{\verb|\tau|} \\
\verb|\upsilon| & \verb|%upsilon| & \ue{\verb|\upsilon|} \\
\verb|\phi| & \verb|%phi| & \ue{\verb|\phi|} \\
\verb|\chi| & \verb|%chi| & \ue{\verb|\chi|} \\
\verb|\psi| & \verb|%psi| & \ue{\verb|\psi|} \\
\verb|\omega| & \verb|%omega| & \ue{\verb|\omega|} \\
\verb|\Gamma| & \verb|%Gamma| & \ue{\verb|\Gamma|} \\
\verb|\Delta| & \verb|%Delta| & \ue{\verb|\Delta|} \\
\verb|\Theta| & \verb|%Theta| & \ue{\verb|\Theta|} \\
\verb|\Lambda| & \verb|%Lambda| & \ue{\verb|\Lambda|} \\
\verb|\Xi| & \verb|%Xi| & \ue{\verb|\Xi|} \\
\verb|\Pi| & \verb|%Pi| & \ue{\verb|\Pi|} \\
\verb|\Sigma| & \verb|%Sigma| & \ue{\verb|\Sigma|} \\
\verb|\Upsilon| & \verb|%Upsilon| & \ue{\verb|\Upsilon|} \\
\verb|\Phi| & \verb|%Phi| & \ue{\verb|\Phi|} \\
\verb|\Psi| & \verb|%Psi| & \ue{\verb|\Psi|} \\
\verb|\Omega| & \verb|%Omega| & \ue{\verb|\Omega|} \\
\hline
\hline
\end{tabular}

\subsection*{Configurable Symbols}

If you have used \verb|\assumeSymbol| to assign meanings to certain inputs symbols,
then they will be mapped into corresponding Maxima forms:

\begin{tabular}{|c|c|c|}
\hline
LaTeX input & Maxima form & Live example \\
\hline
\verb|\assumeSymbol{e}{exponentialNumber} $e$| & \verb|%e| & \ue{\verb|\assumeSymbol{e}{exponentialNumber} $e$|} \\
\verb|\assumeSymbol{i}{imaginaryNumber} $i$| & \verb|%i| & \ue{\verb|\assumeSymbol{i}{imaginaryNumber} $i$|} \\
\verb|\assumeSymbol{\pi}{constantPi} $\pi$| & \verb|%pi| & \ue{\verb|\assumeSymbol{\pi}{constantPi} $\pi$|} \\
\verb|\assumeSymbol{\gamma}{eulerGamma} $\gammai$| & \verb|%gamma| & \ue{\verb|\assumeSymbol{\gamma}{eulerGamma} $\pi$|} \\
\verb|\assumeSymbol{f}{function} $f(x)$| & \verb|f(x)| & \ue{\verb|\assumeSymbol{f}{function} $f(x)$|} \\
\verb|\assumeSymbol{f}{function} $f^2(x)$| & \verb|f(x)^2| & \ue{\verb|\assumeSymbol{f}{function} $f^2(x)$|} \\
\verb|\assumeSymbol{f}{function} $f^{-1}(x)$| & \verb|inverse[f](x)| & \ue{\verb|\assumeSymbol{f}{function} $f^{-1}(x)$|} \\
\hline
\end{tabular}

Note that Maxima does not actually have a notation for inverse functions, hence
the fictitional \verb|inverse[f]| construct above. You can change the name of
this ``function'' using
\verb|\setUpConversionOption{maximaInverseFunction}{name}|.

\subsection*{Other Supported Constructs}

\begin{itemize}
\item
  Units entered using the special SnuggleTeX \verb|\units| macro, such as
  \verb|\units{kg}| generate a Maxima form like \verb|units("kg")|, which
  is similar to how we handle unapplied operators. The name of the
  resulting function can be specified with
  \verb|\setUpConversionOption{maximaUnitsFunction}{name}|.

\item
  Subscripted identifiers are converted to a suitable Maxima form if
  deemed possible.

  \ue{\verb|A_{i,j}x_j|}
  \ue{\verb|x_{i,j_{n,m_2}}|}

\end{itemize}

