\pageId{download}

\subsection*{Download from Sourceforge.net}

You can \href[download]{http://sourceforge.net/project/showfiles.php?group_id=221375}
any of the SnuggleTeX ZIP distributions from SourceForge.net. We currently offer two
flavours:

\begin{itemize}
  \item \verb|snuggletex-n.n.n-basic.zip| is a basic binary distribution containing
    everything you need for SnuggleTeX's core functionality, allowing
    you to convert LaTeX to XHTML/MathML. No further JAR files
    are required for this.

  \item \verb|snuggletex-n.n.n-full.zip| is the full distribution containing
    all SnuggleTeX code module binariees, all optional dependency JARs and the
    SnuggleTeX source code. Use this one if you additionally want to do look at the
    source,
    \href[convert LaTeX to XHTML+images]{docs://legacyWebPages},
    or use the \href[semantic enrichment]{docs://upconversion}
    to generate Content MathML and/or Maxima syntax.
\end{itemize}

You can also download SnuggleTeX development snapshots from its
\href[Subversion repository]{http://sourceforge.net/scm/?type=svn&group_id=221375}
if you enjoy living on the edge! You will need
\href[Apache Maven]{http://maven.apache.org/} to build SnuggleTeX from source.

\subsection*{Maven Users}

If you are using \href[Apache Maven]{http://maven.apache.org/} then you can
automatically obtain SnuggleTeX artifacts (starting from 1.1.0-beta1)
from the following repository:

\begin{verbatim}<repository>
  <id>www2.ph.ed.ac.uk-releases</id>
  <url>http://www2.ph.ed.ac.uk/maven2</url>
</repository>\end{verbatim}

where you will find the following:

\begin{verbatim}<dependency>
  <groupId>uk.ac.ed.ph.snuggletex</groupId>
  <artifactId>snuggletex-core</artifactId>
  <version>...</version>
</dependency>
<dependency>
  <groupId>uk.ac.ed.ph.snuggletex</groupId>
  <artifactId>snuggletex-upconversion</artifactId>
  <version>...</version>
</dependency>
<dependency>
  <groupId>uk.ac.ed.ph.snuggletex</groupId>
  <artifactId>snuggletex-jeuclid</artifactId>
  <version>...</version>
</dependency>\end{verbatim}

Consult the Maven documentation for instructions on setting up your \verb|pom.xml|
as appropriate.
