\pageId{domOutput}

The simplest outputs that SnuggleTeX can create are XML String and XML
DOM-based outputs.

\subsection*{Usage}

\begin{itemize}
  \item
    Call one of the \verb|SnuggleSession.buildXMLString()| methods create an XML String
    fragment (or, more formally, a ``well-formed external general parsed entity'')
    representing everything that has been parsed so far.  This type of output
    can be useful for demonstrating results, or if you need to pass or transmit
    the resulting XML to other software components.
    (See the \href[Minimal]{docs://firstExample} and \href[XML String Output]{docs://xmlStringOutputExample}
    examples to demonstrate this.)

  \item
    Call one of the \verb|snuggleSession.buildDOMSubtree()|
    methods to append the resulting XML to an existing DOM \verb|Element|'s
    children. This might be useful if you are integrating SnuggleTeX into some
    other activity that builds a DOM.

  \item
    Call one of the \verb|snuggleSession.buildDOMSubtree()|
    methods to create a new \verb|Document| and return a \verb|NodeList|
    representing your converted LaTeX inputs. (Note that SnuggleTeX will wrap
    these Nodes within a special root \verb|Element| within the
    \verb|Document|.)

\end{itemize}

\subsection*{Output Configuration}

You can configure exactly how this works using a \verb|DOMOutputOptions| Object
for DOM outputs or its subclass \verb|XMLStringOutputOptions| Object for XML String
outputs. These are both simple JavaBeans that let you control details such as:

\begin{itemize}
  \item Prefixing of XHTML, MathML (and SnuggleTeX) XML elements;
  \item Whether to annotate MathML with the LaTeX input;
  \item Whether and how to report any LaTeX errors discovered during processing
    inside the resulting XML output;
  \item What to do with any URLs encountered (e.g. those specified with the \verb|\href| command);
  \item Whether to inline CSS using \verb|style| attributes; (This can be useful if your XML
    is going to end up inside some kind of XML application that doesn't support user-specified
    CSS stylesheets. See \href[CSS Stylesheet Notes]{docs://stylesheets} for more discussion of
    these points.)
  \item Whether you want to ``post-process'' the newly created DOM \verb|Node|s before they get
    added to the final DOM tree;
  \item (For \verb|XMLStringOutputOptions|) How the resulting XML string should be serialized,
    such as control over indentation, encoding, XML declaration, DOCTYPE delcaration and whether
    to use named entities instead of numeric character references. (Note that you will need
    an XSLT 2.0 processor, such as the version of Saxon 9.1 bundled with the full SnuggleTeX
    distribution, if you want to output named entities.)
\end{itemize}

Have a look at the API documentation for \verb|DOMOutputOptions| and
\verb|XMLStringOutputOptions| for more information.
